### 2022-10-29 draft/draft.Rmd
updating accuracy for mbconnectome example

The ASE in two dimensions suggest that the MBM with one dimensional quadratic manifolds is an appropriate model for these graphs (figure \ref{fig:mbconnectome-ase}). 
Fitting two quadratic Bezier curves to the ASEs (figure \ref{fig:mbconnectome-kcurves}) results in 73.3\% accuracy for the left hemisphere connectome and 76.5\% accuracy for the right hemisphere connectome.

@@

```{r mbconnectome-kcurves, fig.cap = 'ASEs of the Drosophila connectome graphs with quadratic Bezier curves fitted via $K$-curves clustering. The embedding vectors are colored by predicted label.', fig.height = 2, fig.width = 8, cache = TRUE}
set.seed(1)

>>>>

The ASE in two dimensions suggest that the MBM with one dimensional quadratic manifolds is an appropriate model for these graphs (figure \ref{fig:mbconnectome-ase}). 
Fitting two quadratic Bezier curves to the ASEs (figure \ref{fig:mbconnectome-kcurves}) results in 78.5\% accuracy for the left hemisphere connectome and 74.6\% accuracy for the right hemisphere connectome.

@@

```{r mbconnectome-kcurves, fig.cap = 'ASEs of the Drosophila connectome graphs with quadratic Bezier curves fitted via $K$-curves clustering. The embedding vectors are colored by predicted label.', fig.height = 2, fig.width = 8, cache = TRUE}
set.seed(12345)
